### 2014-11-12 locks.tex

\paragraph{Locking} The CLM virtual machine uses spin-locks to protect shared data structures between
threads. As described in Section~\ref{sec:implementation}, coordination
operations require synchronization since they need to change node information
and sometimes move nodes between the standard queue and the regular queue.
In order to measure the locking costs of coordination, we measured the following
statistics: \emph{basic locks}, the number of locks acquired that were already
present in the original LM virtual machine and \emph{coordination locks}, the
number of locks acquired for performing coordination operations. We also
measured how often a \texttt{lock()} operation fails on the first attempt, but
such statistics are not represented in the figures below since the values are
too small.

@@

\begin{topfig}
\footnotesize\begin{tabular}{ | l || c | c | c | c | c |}
\hline
\multirow{2}{*}{\textbf{Program}} & \multicolumn{5}{c |}{\textbf{Queue
   Instructions}} \\ \cline{2-6}
& 1 & 2 & 4 & 8 & 16 \\ \hline
\hline
SSSP - Regular & 199K & 201K & 205K & 196K & 207K \\ \hline
SSSP - Coordinated & 964K & 938K & 870K & 886K & 963K \\ \hline
SSSP - Buffered & 1M & 1M & 1M & 1M & 1M \\ \hline
\hline
HT - Buffered & 25M & 32M & 34M & 34M & 36M \\ \hline
HT - Coordinated & 51M & 55M & 85M & 80M & 72M \\ \hline
HT - Local-Only & 51M & 55M & 79M & 74M & 68M \\ \hline
\hline
LBP - Regular & 15M & 17M & 16M & 11M & 8M \\ \hline
SBP - Coordinated & 96M & 97M & 87M & 83M & 77M \\ \hline
\hline
MiniMax - Regular & 16M & 19M & 19M & 19M & 20M \\ \hline
MiniMax - Coordinated & 51M & 51M & 51M & 51M & 52M \\ \hline
\hline
N Queens - Regular & 8K & 15K & 16K & 17K & 20K \\ \hline
N Queens - Coordinated & 57M & 24M & 675K & 145K & 46K \\ \hline
N Queens - Static & 57M & 44M & 1M & 1M & 151K \\ \hline
\hline
\end{tabular}
\scap{queue_instructions}{Number of queue \scare{instructions} per program. An
   operation to a regular queue counts as 1 instruction, while an operation to
   a priority queue costs the number of
   \emph{percolate-up}/\emph{percolate-down} steps performed.}
\end{topfig}

>>>>

\paragraph{Locking} The CLM virtual machine uses spin-locks to protect shared data structures between
threads. As described in \sectref{sec:implementation}, coordination
operations require synchronization since they need to change node information
and sometimes move nodes between the standard queue and the regular queue.
In order to measure the locking costs of coordination, we measured the following
statistics: \emph{basic locks}, the number of locks acquired that were already
present in the original LM virtual machine and \emph{coordination locks}, the
number of locks acquired for performing coordination operations. We also
measured how often a \texttt{lock()} operation fails on the first attempt, but
such statistics are not represented in the figures below since the values are
too small.

@@

\begin{toptab}
\footnotesize\begin{tabular}{ | l || c | c | c | c | c |}
\hline
\multirow{2}{*}{\textbf{Program}} & \multicolumn{5}{c |}{\textbf{Queue
   Instructions}} \\ \cline{2-6}
& 1 & 2 & 4 & 8 & 16 \\ \hline
\hline
SSSP - Regular & 199K & 201K & 205K & 196K & 207K \\ \hline
SSSP - Coordinated & 964K & 938K & 870K & 886K & 963K \\ \hline
SSSP - Buffered & 1M & 1M & 1M & 1M & 1M \\ \hline
\hline
HT - Buffered & 25M & 32M & 34M & 34M & 36M \\ \hline
HT - Coordinated & 51M & 55M & 85M & 80M & 72M \\ \hline
HT - Local-Only & 51M & 55M & 79M & 74M & 68M \\ \hline
\hline
LBP - Regular & 15M & 17M & 16M & 11M & 8M \\ \hline
SBP - Coordinated & 96M & 97M & 87M & 83M & 77M \\ \hline
\hline
MiniMax - Regular & 16M & 19M & 19M & 19M & 20M \\ \hline
MiniMax - Coordinated & 51M & 51M & 51M & 51M & 52M \\ \hline
\hline
N Queens - Regular & 8K & 15K & 16K & 17K & 20K \\ \hline
N Queens - Coordinated & 57M & 24M & 675K & 145K & 46K \\ \hline
N Queens - Static & 57M & 44M & 1M & 1M & 151K \\ \hline
\hline
\end{tabular}
\vspace*{.5ex}
\scap{queue_instructions}{Number of queue \scare{instructions} per program. An
   operation to a regular queue counts as 1 instruction, while an operation to
   a priority queue costs the number of
   \emph{percolate-up}/\emph{percolate-down} steps performed.}
\end{toptab}
